TacticToe: Learning to Prove with Tactics

### 2018-08-24 tactictoe_jv.tex
more

Proof patching \cite{RingerYLG18} is an approach that attempts to learn the
proof changes necessary for a modification of a prover library or system. The
approach is hard to apply for new proofs. Following this idea, \tactictoe
could also try to learn from different versions of the prover library.

>>>>

Proof patching \cite{RingerYLG18} is an approach that attempts to learn the
proof changes necessary for a modification of a prover library or system. This
approach is however hard to use to create completely new proofs. Following this idea, \tactictoe
could try to learn from different versions of the prover library.
